---
title: "Re-write the Lake Huron shiny application"
author: "Yifu Dong"
date: "September 23, 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE}
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE)
```


## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}
 lakehuron <- data.frame(time=1875:1972,lakehurondata=LakeHuron) #dataframe 

inputPanel(
  
  
  checkboxInput("smooth", label = "Add smoother?", value = FALSE)
)

renderPlot({
  
  if(input$smooth){
    ggplot(data=lakehuron)+
        geom_point(mapping=aes(x=time,y=lakehurondata))+
        geom_smooth(mapping = aes(x=time,y=lakehurondata),se=FALSE,color="red")
    }else{
      ggplot(data=lakehuron)+
        geom_point(mapping=aes(x=time,y=lakehurondata))

       }; 
})




```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



